Curve counting in genus one: elliptic singularities and relative geometry

### 2019-06-27 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
Added remark about degree zero reduced rubber for base of induction

The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$, the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces, and the  rubber invariants of $P$ are also given by integrals over Deligne--Mumford spaces, using the formula for the double ramification cycle \cite{Hain,JPPZ} in terms of tautological classes. We will now explain how to perform each of the four inductive steps outlined above.

>>>>

The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$ and the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces. The rubber invariants of $P$ in degree zero are given by integrals over the main component of the double ramification cycle; this can likewise be computed as an integral over Deligne--Mumford space, by correcting the formula for the ordinary double ramification cycle \cite{Hain,JPPZ} by the obvious contribution from the boundary irreducible component (the observation which makes this easy to do in genus one is that the rubber moduli space is pure-dimensional, so that the virtual class is simply the sum of the fundamental classes of the irreducible components). We will now explain how to perform each of the four inductive steps outlined above.
